Human Factors Influencing Visual Statistical Inference

### 2013-06-13 sociology_paper.tex
anova analysis added

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=4in]{demographic_effect.pdf} 
   \caption{Boxplots of average time taken in log scale and proportion correct responses of all the lineups plotted for each demographic factor variables. The dots inside the box represents mean. None of the demographic factors appear to be statistically significant except India effect for proportion correct. Effect of graduate degree in proportion correct is also significant but is actually the India effect since, Most of the graduate degree holders are coming from India.}
   \label{fig:demographic_effect}
\end{figure}

@@

>>>>

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=4in]{demographic_effect.pdf} 
   \caption{Boxplots of average time taken in log scale and proportion correct responses of all the lineups plotted for each demographic factor variables. The dots inside the box represents mean. Demographic factors appear to be statistically significant for explaining time taken. Effect of graduate degree and India in proportion correct is much different but is actually the India effect since, Most of the graduate degree holders are coming from India.}
   \label{fig:demographic_effect}
\end{figure}

@@

\begin{table}[htbp]
\centering
\caption{Anova of full model with all the demographic factors vs reduced model with removing respective factor.}
\begin{tabular}{lrrrrrrrr}
  \hline
Model && Df & AIC & BIC & logLik & Chisq & Chi.Df & $p$-value \\ 
  \hline
Log Time &Full& 16 &  51904.00 &52034.00 & -25936.00 & &  &  \\ 
&Age & 10 & 52435.63 & 52516.41 & -26207.81 & 543.18 & 6 & $<$0.001 \\ 
 & Country & 14 & 52849.92 & 52963.15 & -26410.96 & 949.47 & 2 & $<$0.001 \\ 
  &Education & 12 & 52012.68 & 52109.61 & -25994.34 & 116.23 & 4 & $<$0.001 \\ 
  &Gender & 15 & 51970.57 & 52091.74 & -25970.28 & 68.12 & 1 & $<$0.001 \\ 
\hline
Proportion Correct &Full& 15 & 23822.00 &23943.00 &-11896.00  & &  &  \\ 
  &Age & 9 & 23835.22 & 23907.93 & -11908.61 & 25.50 & 6 & $<$0.001 \\ 
  &Country & 13 & 24099.57 & 24204.72 & -12036.78 & 281.85 & 2 & $<$0.001 \\ 
  &Education & 11 & 23837.48 & 23926.34 & -11907.74 & 23.77 & 4 & $<$0.001 \\ 
  &Gender & 14 & 23821.88 & 23934.98 & -11896.94 & 2.17 & 1 & 0.140 \\ 
   \hline
\end{tabular}
\end{table}
